---
title: "Weight of Fish"
author: "Erika Mondragon"
date: "Fall 2023"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(dplyr)
library(leaps)
fish = read_csv("Fish.csv")
```

# Predicting Fish Weight
Find the best model using two variables to predict Perch weight, and compare this to the best over all model

## Perch

```{r}
perch=filter(fish, Species == "Perch")
```


### Best Two regressor model

```{r}
modelPerch= regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data=perch)
summary(modelPerch)
```


```{r}
best2Perch = lm(Weight ~ Height + Width, data = perch)
summary(best2Perch)
```

## best 2-variable equation
Weight = -536 + 74.77*Height+ 69.62*Width


## Pike
```{r}
pike=filter(fish, Species == "Pike")
```


### Best Two regressor model
```{r}
modelPike= regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data=pike)
summary(modelPike)
```

```{r}
best2Pike = lm(Weight ~ Length1 + Length3, data = pike)
summary(best2Pike)
```
## best 2-variable equation
Weight = -1675.79 + -105.64*Length1+ 141.25*Length3

## Roach
```{r}
roach=filter(fish, Species == "Roach")
```

### Best Two regressor model
```{r}
modelRoach= regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data=roach)
summary(modelRoach)
```

```{r}
best2Roach = lm(Weight ~ Width + Length3, data = roach)
summary(best2Roach)
```

## best 2-variable equation
Weight = -319.118 + -72.300*Width+ 8.278*Length3

## Final Summary Statements
 